---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Justin Mai Quang Truong Le (12559642)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## Exercise 1: Initializing git

### 1d)

Strengths:

-   Decentralization: allows easy collaboration, because every developer has a copy of repository

-   Branching/Merging: You can create branches for independent features or bug fixes without affecting the main branch.\
    Later on you can merge back the branches into the main.

Weakness:

-   Large Files: e.g. Images, videos, ..., will slow down operations (cloning, pushing, pulling). Can be negated but have to be set up first.

-   Difficult for Beginners: Very overwhelming for beginners and might be used conservatively until one is more comfortable with it.

# Exercise 2: Putting your Repository on GitHub

### 2a)

<https://github.com/ju-le19/exeRcise-sheet-3.git>

### Exercise 3: Baby-Names in Munich

### 3b)

```{r}
library(dplyr)

vornamen22 <- read.csv("data/open_data_portal_2022.csv")
vornamen23 <- read.csv("data/vornamen-muenchen-2023.csv")

# class(vornamen22$Anzahl) shows character
# class(vornamen23$Anzahl) shows character
# looking through data set you can find that all counts less than 4 are written as "4 oder weniger"

vornamen22 <- vornamen22 %>%
  mutate(Anzahl = as.numeric(gsub("[^0-9]", "", Anzahl)))

vornamen23 <- vornamen23 %>%
  mutate(Anzahl = as.numeric(gsub("[^0-9]", "", Anzahl)))

head(vornamen22, 3)
head(vornamen23, 3)
```

Because I do not have more info about "4 oder weniger", I decided for the simplest solution which was to remove any non numeric character and convert the column to numeric afterwards.

Obviously the consequence of this is that now all counts of names that are less or equal to 4 aren't correctly represented in the dataset.

### 3c)

```{r}
total_babies_2022 <- vornamen22 %>%
  summarize(total = sum(Anzahl, na.rm = TRUE)) %>%
  pull(total)

total_babies_2023 <- vornamen23 %>%
  summarize(total = sum(Anzahl, na.rm = TRUE)) %>%
  pull

cat("2022: ", total_babies_2022, "\n")
cat("2023: ", total_babies_2023, "\n")
```

More babies were born in the year 2022.

### 3d)

```{r}
vornamen22 <- mutate(vornamen22, year = 2022)
vornamen23 <- mutate(vornamen23, year = 2023)

str(vornamen22)
str(vornamen23)
```

### 3e)

```{r}
combined_vorname <- bind_rows(vornamen22, vornamen23)

str(combined_vorname)
```

### 3f)

```{r}
library(knitr)

popularity <- combined_vorname %>%
  group_by(Vorname) %>%
  summarize(Total_Count = sum(Anzahl)) %>%
  arrange(desc(Total_Count))

kable(head(popularity, 10), caption = "Top 10 Most Popular Names Across Both Years")
```
