---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Justin Mai Quang Truong Le (12559642)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## Exercise 1: Initializing git

### 1d)

Strengths:

-   Decentralization: allows easy collaboration, because every developer has a copy of repository

-   Branching/Merging: You can create branches for independent features or bug fixes without affecting the main branch.\
    Later on you can merge back the branches into the main.

Weakness:

-   Large Files: e.g. Images, videos, ..., will slow down operations (cloning, pushing, pulling). Can be negated but have to be set up first.

-   Difficult for Beginners: Very overwhelming for beginners and might be used conservatively until one is more comfortable with it.

# Exercise 2: Putting your Repository on GitHub

### 2a)

<https://github.com/ju-le19/exeRcise-sheet-3.git>

### Exercise 3: Baby-Names in Munich

### 3b)

```{r}
library(dplyr)

vornamen22 <- read.csv("data/open_data_portal_2022.csv")
vornamen23 <- read.csv("data/vornamen-muenchen-2023.csv")

# class(vornamen22$Anzahl) shows character
# class(vornamen23$Anzahl) shows character
# looking through data set you can find that all counts less than 4 are written as "4 oder weniger"

vornamen22 <- vornamen22 %>%
  mutate(Anzahl = as.numeric(gsub("[^0-9]", "", Anzahl)))

vornamen23 <- vornamen23 %>%
  mutate(Anzahl = as.numeric(gsub("[^0-9]", "", Anzahl)))

head(vornamen22, 3)
head(vornamen23, 3)
```

Because I do not have more info about "4 oder weniger", I decided for the simplest solution which was to remove any non numeric character and convert the column to numeric afterwards.

Obviously the consequence of this is that now all counts of names that are less or equal to 4 aren't correctly represented in the dataset.

### 3c)

```{r}
total_babies_2022 <- vornamen22 %>%
  summarize(total = sum(Anzahl, na.rm = TRUE)) %>%
  pull(total)

total_babies_2023 <- vornamen23 %>%
  summarize(total = sum(Anzahl, na.rm = TRUE)) %>%
  pull

cat("2022: ", total_babies_2022, "\n")
cat("2023: ", total_babies_2023, "\n")
```

More babies were born in the year 2022.

### 3d)

```{r}
vornamen22 <- mutate(vornamen22, year = 2022)
vornamen23 <- mutate(vornamen23, year = 2023)

str(vornamen22)
str(vornamen23)
```

### 3e)

```{r}
combined_vorname <- bind_rows(vornamen22, vornamen23)

str(combined_vorname)
```

### 3f)

```{r}
library(knitr)

popularity <- combined_vorname %>%
  group_by(Vorname) %>%
  summarize(Total_Count = sum(Anzahl)) %>%
  arrange(desc(Total_Count))

kable(head(popularity, 10), caption = "Top 10 Most Popular Names Across Both Years")
```

## Exercise 4: Open Analysis

### 4c)

Dataset Name: CO2 emissions by city - C40 Cities (2018)

Link: [https://github.com/owid/owid-datasets/blob/master/datasets/CO2%20emissions%20by%20city%20-%20C40%20Cities%20(2018)/CO2%20emissions%20by%20city%20-%20C40%20Cities%20(2018).csv](https://github.com/owid/owid-datasets/blob/master/datasets/CO2%20emissions%20by%20city%20-%20C40%20Cities%20(2018)/CO2%20emissions%20by%20city%20-%20C40%20Cities%20(2018).csv){.uri}

### 4d)

Research Question: What is the distribution of CO2 emissions among cities in the C40 network? Are there any significant differences in emissions levels between the cities?

This questions is interesting because it allows us observe how fair they well in their cause and we might find common patterns of eg. policies, ... that caused their situation (positive and negative.

### 4e)

```{r}
library(ggplot2)

co2_emissions <- read.csv("data/CO2 emissions by city - C40 Cities (2018).csv")

summary(co2_emissions$CO2.emissions.per.capita)

ggplot(co2_emissions, aes(x = CO2.emissions.per.capita)) +
  geom_histogram(binwidth = 5, fill = "skyblue", color = "black") +
  labs(title = "Distribution of CO2 Emissions per Capita",
       x = "CO2 Emissions per Capita (metric tons)",
       y = "Frequency") +
  theme_minimal()

mean_emissions <- co2_emissions %>%
  group_by(Entity) %>%
  summarize(mean_co2 = mean(CO2.emissions.per.capita, na.rm = TRUE))

summary(mean_emissions$mean_co2)
```

We can observe that the majority of the cities have a lower CO2 emissions per capita that somewhat model a gaussian-like distribution around the median and mean. We can see that all cities but one can be found clustered around these values.

The outlier being Melbourne with 37.660 metric tons. This suggests with an exceptionally high CO2 emissions per capita we can try to understand and learn from Melbourne to find reasons why this is the case, e.g. industrial activity, infrastructure, energy consumption or unique characteristecs of the city.\

So the answer to the questions is that there are indeed differences in emissions levels between cities in the C40 network.
